% class
\documentclass[a4paper, 11pt]{article}

% packages
	% margins and layout
		\usepackage[bottom = 1.5cm, top = 1.5cm, left = 1.5cm, right = 1.5cm]{geometry}
	% fonts/language
		\usepackage[utf8]{inputenc}
		\usepackage[T1]{fontenc}
		\usepackage[english]{babel}
		\usepackage{fontawesome5}
	% titles
		\usepackage{titlesec}
	% color
		\usepackage{xcolor}
	% itemize/enumerate
		\usepackage{enumitem}
	% url/hyperlinks
		\usepackage[colorlinks = true, linkcolor = black, citecolor = black, urlcolor = black]{hyperref}
	% tables
		\usepackage{tabularx}
	% math
		\usepackage{mathtools}
		\usepackage{amssymb}
	% other 
		% \usepackage{verbatim}
		\usepackage{scalerel}	% scalebox
		\usepackage{textpos}	% environment textblock

% layout
	% pagestyle
	\pagestyle{empty}
	% table settings
	\setlength{\tabcolsep}{0cm}
	% sections formatting
	\titleformat{\section}%
		{\vspace{-4pt}\scshape\raggedright\large}{}{0em}{}%
		[\color{black}\titlerule\vspace{-3pt}]
	% other
		% ensure that generate pdf is machine readable/ATS parsable
			\pdfgentounicode = 1
		% remove indentation
		\newlength\tindent
		\setlength{\tindent}{\parindent}
		\setlength{\parindent}{0pt}
		\renewcommand{\indent}{\hspace*{\tindent}}

% commands
	% cv items
		\newcommand{\cvitemstart}{\begin{itemize}}
		\newcommand{\cvitemend}{\end{itemize}\vspace{-5pt}}
		\newcommand{\cvitem}[1]{%
			\item \small{{#1 \vspace{-1pt}}}
		}
	% cv headings
		\newcommand{\cvsubheadingstart}{%
			\begin{itemize}[leftmargin = 0cm, label = {}]
		}
		\newcommand{\cvsubheadingend}{\end{itemize}}
		\newcommand{\cvsubheading}[4]{
			\vspace{-4pt}
			\item
				\begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
					\textbf{#1} & #2 \\
					\textit{\small #3} & \textit{\small #4} \\
				\end{tabular*}\vspace{-7pt}
		}
		\newcommand{\cvresearchheading}[3]{
			\vspace{-4pt}
			\item
				\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
					\textbf{#1} & \\
					\textit{\small #2} & \textit{\small #3} \\  
				\end{tabular*}\vspace{-7pt}
		}
	% cv skills
		\newcommand{\cvskills}[1]{
			\begin{itemize}[leftmargin = 0cm, label = {}]
				\small{\item{
					#1
				}}
			\end{itemize}
		}
		\newcommand{\cvsep}{\kern2pt$|$\kern2pt \ }
	% markers
		\newcommand{\squaremarker}{\raisebox{0.07cm}{\scalebox{0.25}{\faSquare}}}
		\newcommand{\roundmarker}{\raisebox{0.07cm}{\scalebox{0.25}{\faCircle}}}
		\renewcommand\labelitemii{\squaremarker}
	% symbols
		\newcommand{\addsymbol}[1]{\scalebox{0.8}{#1}\kern5pt}
	% info
		% mail
		\newcommand{\addmail}{%
			\addsymbol{\faAt} \href{mailto:francescocaporali@outlook.com}{francescocaporali@outlook.com}
		}
		% institutional mail
		\newcommand{\addinstitutionalmail}{%
			\addsymbol{\faAt} \href{mailto:fc4978@princeton.edu}{fc4978@princeton.edu}
		}
		% phone
		\newcommand{\addphone}{%
			\addsymbol{\faPhone*} $+1 \ (609) \, 786 \, 0295$
		}
		% homepage
		\newcommand{\addhomepage}{%
			\addsymbol{\faGlobe} \href{https://caporali.github.io/}{caporali.github.io}
		}
		% linkedin
		\newcommand{\addlinkedin}{%
			\addsymbol{\faLinkedin} \href{https://www.linkedin.com/in/francescocaporali/}{francescocaporali}
		}
		% github
		\newcommand{\addgithub}{%
			\addsymbol{\faGithub} \href{https://github.com/caporali}{caporali}
		}
		% address
		\newcommand{\addaddress}{%
			\addsymbol{\faMapMarker*} 224 - Sherrerd Hall, Princeton (NJ), 08540, USA 
		}
		% link
		\newcommand{\addlink}{%
			\addsymbol{\faLink}
		}
	% last updated
	\newcommand{\lastupdated}{
		\begin{textblock*}{\textwidth}(0cm, -0.6cm)
			{\color{gray} \footnotesize
			\hfill \addsymbol{\faCalendar[regular]} Last updated: \today}
		\end{textblock*}
	}

% main

\begin{document}

	% heading
	{\Huge\textsc{Francesco \textbf{Caporali}}} \lastupdated
	\vskip 10pt
	{\small
		\begin{tabular*}{0.99\textwidth}{l @{\extracolsep{\fill}} l @{\extracolsep{\fill}} l}
			\addmail & \addinstitutionalmail & \addphone \\
			\addaddress & \addhomepage & \addlinkedin \\
		\end{tabular*}		
	}

	% education
	\section{Education}
		\cvsubheadingstart
			% phd orfe, princeton
				\cvsubheading{Ph.D. in Operations Research and Financial Engineering}%
				{Princeton University}%
				{Princeton (NJ), USA}%
				{August 2024 $-$ Ongoing}
				\cvitemstart
					\cvitem{\textit{Advisor:} Prof. Boris Hanin.}
				\cvitemend
			% msc math, unito
			\cvsubheading{M.Sc. in Stochastics and Data Science (Mathematics)}%
				{University of Turin}%
				{Turin, Italy}%
				{September 2022 $-$ July 2024}
				\cvitemstart
					\cvitem{Final grade: $110/110$ cum laude and special mention.}
					\cvitem{
						\textbf{Thesis:} Student-\texorpdfstring{$t$}{t} processes as infinite-width limits of posterior Bayesian Neural Networks \\
						\textit{Advisor:} Prof. Stefano Favaro and Prof. Dario Trevisan
					} 
				\cvitemend
			% msc stat/applied math, cca
			\cvsubheading{M.Sc. in Statistics and Applied Mathematics}%
				{Collegio Carlo Alberto}%
				{Turin, Italy}%
				{September 2022 $-$ July 2024}
				\cvitemstart
					\cvitem{\textit{Allievi Honors Program} full scholarship. Competitive admission to a study program in applied mathematics and statistics. The Allievi are admitted after a nationwide selection.}
				\cvitemend
			% bsc math, unipi
			\cvsubheading{B.Sc. in Mathematics (computational curriculum)}%
				{University of Pisa}%
				{Pisa, Italy}%
				{September 2018 $-$ May 2022}
				\cvitemstart
					\cvitem{Final grade: $110/110$ cum laude.}
					\cvitem{
						\textbf{Thesis:} Deep Neural Networks: approximation capabilities and Gaussian behaviour \\
						\textit{Advisor:} Prof. Dario Trevisan
					} 
					
				\cvitemend
			% \vspace{4pt}
			% % high school diploma
			% \cvsubheading{High school diploma}%
			% 	{Liceo Scientifico Paolo Ruffini}%
			% 	{Viterbo, Italy}%
			% 	{September 2013 $-$ July 2018}
			% 	\cvitemstart
			% 		\cvitem{Final grade: $100/100$.}
			% 	\cvitemend
		\cvsubheadingend
		\vspace{-17pt}

	% academic interests
	\section{Academic Interests}
		\begin{itemize}[leftmargin = 0cm, label = {}]
			\small{\item{
			My research lies at the intersection of probabilistic ML and optimization dynamics. 
			I am currently interested in analyzing the stability and implicit bias of GD/SGD and designing principled noise, clipping, and step-size schedules for reliable training. 
			Previously, I studied Bayesian neural networks and their infinite-width/posterior limits to characterize uncertainty and robustness.
			}}
		\end{itemize}
		\vspace{-18pt}

	% research
	\section{Research}
		\cvsubheadingstart
			\cvresearchheading{\href{https://openreview.net/pdf?id=iUppQcPAMK}{Student-\texorpdfstring{$t$}{t} processes as infinite-width limits of posterior Bayesian NNs}}%
				{\textit{F. Caporali}, S. Favaro, D. Trevisan}%
				{TASC workshop, COLT 2025}%
				\cvitemstart
					\cvitem{Showed that Bayesian Neural Networks with Gaussian priors on weights and Inverse-Gamma priors on variances converge to Student-t processes in the infinite-width limit.}
				\cvitemend
		\cvsubheadingend
		\vspace{-17pt}

	% conferences and workshops
	\section{Conferences and workshops}
		\cvsubheadingstart
			% g-research
			\cvsubheading{G-Research, Spring into Quant Finance}%
				{G-Research}%
				{Palermo, Italy}%
				{April 2026}
			% conference, colt 2025
			\cvsubheading{38th Annual Conference on Learning Theory (COLT 2025)}%
				{}%
				{Lyon, France}%
				{June 2025}
			% summer school, malga/unige
			\cvsubheading{Summer School ``Topics in Modern Machine Learning''}%
				{University of Genoa}%
				{Genoa, Italy}%
				{June 2023}
			% winter school, unitn
			\cvsubheading{Winter School ``Stochastic Processes, Analysis and Semigroups''}%
				{University of Trento/Wuppertal}%
				{Trento, Italy}%
				{December 2022}
		\cvsubheadingend
		\vspace{-13pt}

	% working experience
	\section{Working experience}
		\cvsubheadingstart
			% applied scientist intern, aws
			\cvsubheading{Applied Scientist Intern}%
				{AWS AI Labs}%
				{Santa Clara, CA, USA}%
				{June $-$ August 2026}
			\vspace{2pt}
			% phc admin, unipi
			\cvsubheading{PHC System administrator}%
				{University of Pisa}%
				{Pisa, Italy}%
				{December 2018 $-$ May 2022}
				\cvitemstart
					\cvitem{Maintained Linux lab network and departmental \href{http://poisson.phc.dm.unipi.it}{\textit{web server}} serving mathematics students.}
				\cvitemend
		\cvsubheadingend
		\vspace{-16pt}

	% projects
	\section{Projects}
		\cvsubheadingstart
			% msc
			\cvsubheading{Master's projects}%
				{University of Turin and Collegio Carlo Alberto}%
				{Turin, Italy}%
				{2022 $-$ 2023}
				\cvitemstart
					\cvitem{\href{https://github.com/caporali/machine_learning_project}{\textit{Machine Learning}}: implementation of GANs from scratch for image generation.}
					\cvitem{\href{https://github.com/caporali/keep_heading_north}{\textit{Algorithms}}: design of a text-based game on a graph with RL integration.}
				\cvitemend
		\cvsubheadingend
		\vspace{-16pt}

	% teaching
	\section{Teaching}
		\cvsubheadingstart
			% teaching assistant, princeton
			\cvsubheading{Teaching Assistant}%
				{Princeton University}%
				{Princeton, NJ, USA}%
				{September 2025 $-$ Ongoing}
				\cvitemstart
					\cvitem{\textit{Probability Theory (ORF526)}, Fall 2025.} 
					\cvitem{\textit{Probability and Stochastic Systems (MAT380/ORF309/EGR309)}, Spring 2026.} 
				\cvitemend
			\vspace{2pt}
			% tutor, unito
			\cvsubheading{Tutorial teaching}%
				{University of Turin}%
				{Turin, Italy}%
				{March $-$ June 2023}
				\cvitemstart
					\cvitem{Tutorial Instructor, \textit{Probability and Statistics} (B.Sc. Mathematics for Finance and Insurance).} 
				\cvitemend
		\cvsubheadingend
		\vspace{-16pt}

	% skills
	\section{Skills}
		\cvskills{%
			% languages
			\textbf{Languages}
				\begin{itemize}[noitemsep, topsep = -2pt]
					\item \textit{Italian:} native.
					\item \textit{English:} advanced level.
				\end{itemize}
			% programming languages
			\textbf{Programming languages}
				\begin{itemize}[noitemsep, topsep = -2pt]
					\item
						Python (PyTorch, Pyro, pandas, scikit-learn, \dots) \cvsep
						R \cvsep
						Matlab \cvsep
						C\textbackslash C++ \cvsep
						SQL (basic) \cvsep
						Julia (basic)
				\end{itemize}
			% markup languages
			\textbf{Markup languages}
				\begin{itemize}[noitemsep, topsep = -2pt]
					\item
						\LaTeX \ \cvsep
						HTML (basic)
				\end{itemize}
			% other computer skills
			\textbf{Other computer skills}
				\begin{itemize}[noitemsep, topsep = -2pt]
					\item Operating systems: Linux (all major distributions), Windows, macOS.
					\item Microsoft Office.
				\end{itemize}				
		}

\end{document}
